InteroceptionScale - Study 1: Data Analysis

### 2025-07-01 paper/manuscript.tex
lesgoo

\title{\textbf{The MInt Scale: A Fresh Validation of the
Multidimensional Interoception Questionnaire Outperforms the MAIA, BPQ
and IAS}}

\shorttitle{MInt Validation}

@@

\keywords{Interoception questionnaire, interoceptive accuracy scale,
MAIA, MInt Validation, Body Awareness}

\authornote{\par{\addORCIDlink{Dominique
Makowski}{0000-0001-5375-9967}}\par{\addORCIDlink{Ana
Neves}{0009-0006-0020-7599}}\par{\addORCIDlink{Giulia
Poreiro}{0000-0002-2343-5109}} 
\par{ }
\par{     \begin{tcolorbox}[enhanced jigsaw, toprule=.15mm, opacityback=0, colframe=quarto-callout-note-color-frame, left=2mm, arc=.35mm, colback=white, bottomrule=.15mm, breakable, rightrule=.15mm, leftrule=.75mm]

@@

\section{Study 1}\label{study-1}

@@

We recruited 760 English-speaking participants using
Prolific\textcopyright. We excluded 191 for failing at least one
attention check, and 10 based on measures significantly related to the
probability of failing attention checks (namely, the multivariate
distance obtained with the OPTICS algorithm,
\citeproc{ref-theriault2024check}{Thériault et al., 2024}). The final
sample includes 559 participants (age = 37 \(\pm\) 12.2 {[}18, 77{]};
50.8\% women; Country of residence: 63.86\% United Kingdom, 26.65\%
United States). This study was approved by the University of Sussex'
Ethics Committee (\textbf{NUMBER}).

@@

Based on the two goals outlined for this scale, namely to include
different interoceptive modalities, and to explicitly state the context
of the interoceptive experience (e.g., whether negative or positive), we
generated items following a combinatorial approach, where each item's
category was a combination of a specific modality and context
(Figure~\ref{fig-one}).

@@

Participants were randomly assigned to one of three conditions, driving
how items were grouped on the same page: 1) items grouped by modality
(i.e., all cardiac items on the first page, all colon \& bladder items
on the second, etc.), 2) items grouped by facet, or 3) items presented
fully randomly (but balanced randomly across 6 pages). The order of the
item on any given page and the order of the modalities/facets were
randomized. Each participant completed the full set of 120 items, with
the attention check items interspersed throughout. The online experiment
was implemented using JsPsych (\citeproc{ref-de2015jspsych}{De Leeuw,
2015}), and item responses were recorded using 7-points Likert scales (0
= Disagree, 6 = Agree).

@@

@@

The correlation matrix similarity analysis yielded no significant
differences between the similarity of the random-grouping condition with
the modality-grouping and facet-grouping conditions
(\(PSI_{\text{Random vs. Facet}} = 0.81\),
\(PSI_{\text{Random vs. Modality}} = 0.82\), \(p = .51\);
\(RVadj_{\text{Random vs. Facet}} = 0.77\),
\(RVadj_{\text{Random vs. Modality}} = 0.78\), \(p = .78\);
\(SMI_{\text{Random vs. Facet}} = 0.49\),
\(SMI_{\text{Random vs. Modality}} = 0.51\), \(p = .55\)).

@@

\section{Study 2}\label{study-2}

TODO: write intro. Goal of study 2: to validate the MInt scale against
other interoception scales.

@@

\phantomsection\label{refs}
\begin{CSLReferences}{1}{0}
\bibitem[\citeproctext]{ref-de2015jspsych}
De Leeuw, J. R. (2015). jsPsych: A JavaScript library for creating
behavioral experiments in a web browser. \emph{Behavior Research
Methods}, \emph{47}, 1--12.

@@

>>>>

\title{\textbf{The Mint Scale: A Fresh Validation of the Multimodal
Interoception Questionnaire and Comparison to the MAIA, BPQ and IAS}}

\shorttitle{Mint Validation}

@@

\keywords{Interoception questionnaire, interoceptive accuracy scale,
MAIA, Mint Validation, Body Awareness}

\authornote{\par{\addORCIDlink{Dominique
Makowski}{0000-0001-5375-9967}}\par{\addORCIDlink{Ana
Neves}{0009-0006-0020-7599}}\par{\addORCIDlink{Giulia
Poreiro}{0000-0002-2343-5109}} 
\par{ }
\par{     \begin{tcolorbox}[enhanced jigsaw, colframe=quarto-callout-note-color-frame, toprule=.15mm, arc=.35mm, left=2mm, breakable, colback=white, rightrule=.15mm, bottomrule=.15mm, leftrule=.75mm, opacityback=0]

@@

\section{Study 1: Item Selection}\label{study-1-item-selection}

@@

We recruited 760 English-speaking participants using
Prolific\textcopyright. We excluded 191 for failing at least one
attention check, and 10 based on measures significantly related to the
probability of failing attention checks (namely, the multivariate
distance obtained with the OPTICS algorithm,
\citeproc{ref-theriault2024check}{Thériault et al., 2024}). The final
sample includes 559 participants (age = 37.0 \(\pm\) 12.2 {[}18, 77{]};
50.8\% women; Country of residence: 63.86\% UK, 26.65\% USA). This study
was approved by the University of Sussex' Ethics Committee
(\textbf{NUMBER}).

@@

Based on the two goals outlined for this scale, namely to include
different interoceptive modalities, and to explicitly state the context
of the interoceptive experience (e.g., whether negative or positive), we
generated items in a systematic way following a combinatorial approach,
where each item's category was a combination of a specific modality and
context (Figure~\ref{fig-one}).

@@

To avoid presenting all the 120 items on a single long and discouraging
page, we split them into different pages. Participants were randomly
assigned to one of three conditions, driving how items were grouped on
the same page: 1) items grouped by modality (i.e., all cardiac items on
the first page, all colon \& bladder items on the second, etc.), 2)
items grouped by facet, or 3) items presented fully randomly (but
balanced randomly across 6 pages). The order of the item on any given
page and the order of the modalities/facets were randomized. Each
participant completed the full set of 120 items, with the attention
check items interspersed throughout. The online experiment was
implemented using JsPsych (\citeproc{ref-de2015jspsych}{De Leeuw,
2015}), and item responses were recorded using 7-points Likert scales (0
= Disagree, 6 = Agree).

@@

Items deemed ``redundant'' (which can distort the item structure
estimation by introducing multicollinearity or local dependencies) will
be identified (using the recommended threshold of 0.25) using Unique
Variable Analysis (UVA, \citeproc{ref-christensen2023unique}{Christensen
et al., 2023}), a novel and principled method derived from network
psychometrics.

The structure of the items will be analyzed using the recently-developed
Exploratory Graph Analysis (EGA, \citeproc{ref-golino2017exploratory}{H.
F. Golino \& Epskamp, 2017}) framework, which allows to jointly estimate
the number of dimensions (i.e., clusters of items), the structure, as
well as its stability using bootstrapping
(\citeproc{ref-golino2020investigating}{H. Golino et al., 2020}). At a
fundamental level, EGA conceptualizes variables as nodes in a network,
with connections (edges) reflecting associations between them. Evidence
has underlined its suitability as an alternative to traditional factor
analysis, addressing some of its limitations such as the assumption of a
``latent'' source of variability, issues in estimation of the optimal
factor numbers, and poor performance in complex population structures,
while remaining comparable and interpretable
(\citeproc{ref-christensen2021equivalency}{Christensen \& Golino, 2021};
\citeproc{ref-jimenez2023dimensionality}{Jiménez et al., 2023}). In
particular, nodes communities (i.e., clusters of items) can be in
practice interpreted as distinct ``dimensions'', similarly to
traditional latent factors - but without explicitly assuming their
existence (\citeproc{ref-christensen2021equivalency}{Christensen \&
Golino, 2021}).

After removing redundant items using UVA, we will iteratively fit
hierarchical EGA models (which additionally estimates higher-order
``meta'' clusters) using ``glasso'' {[}\textbf{REF}{]} and the
``leiden'' algorithm {[}\textbf{REF}{]} for community detection,
refining the item pool at each step. We will start by removing items
with a low (\textless{} 80\%) cluster stability (i.e., volatile items
which jump between clusters across bootstrapped samples), followed by
odd items belonging to no clusters or pairs of items (i.e., we keep
items belonging to clusters of more than 2 items). Finally, for each
lower-level cluster, we will select the 3 items with the highest node
centrality (i.e., the highest loading in the cluster).

@@

The correlation matrix similarity analysis yielded no significant
differences between the similarity of the random-grouping condition with
the modality-grouping and facet-grouping conditions
(\(PSI_{\text{Random vs. Facet}} = 0.81\),
\(PSI_{\text{Random vs. Modality}} = 0.82\), \(p = .45\);
\(RVadj_{\text{Random vs. Facet}} = 0.77\),
\(RVadj_{\text{Random vs. Modality}} = 0.78\), \(p = .74\);
\(SMI_{\text{Random vs. Facet}} = 0.49\),
\(SMI_{\text{Random vs. Modality}} = 0.51\), \(p = .52\)).

From the 120 initial items, UVA flagged 4 redundant items that we
removed. We then removed 40 items that showed low cluster stability, and
9 items that were part of clusters with less than 3 items. Finally, We
kept the 3 items with the highest loading in their lower-level structure
(removing 13 items in the process), resulting in 54 items in the final
item pool.

The final hierarchical EGA model (Generalized Total Entropy Fit Index =
-119.18) - in which all 54 items yielded a high cluster stability
(\textgreater{} 90\%) suggested 3 metaclusters and 15 lower-level
clusters (each containing 3 items): ``Interoceptive Deficits''
(containing 5 clusters: \emph{Urointestinal Inaccuracy} - UrIn;
\emph{Cardiorespiratory Confusion} - CaCo; \emph{Cardiorespiratory
Noticing} - CaNo; \emph{Olfactory Compensation} - Olfa; \emph{Satiety
Noticing} - Sati), ``Interoceptive Awareness'' (containing 7 clusters:
\emph{Sexual Arousal Awareness} - SexA; \emph{Sexual Arousal
Sensitivity} - SexS; \emph{Sexual Organs Sensitivity} - SexO;
\emph{Urointestinal Sensitivity} - UrSe; \emph{Relaxation Awareness} -
RelA; \emph{State Specificity} - StaS; \emph{Expulsion Accuracy} -
ExAc), and ``Interoceptive Sensitivity'' (containing 6 clusters:
\emph{Cardioception} - Card; \emph{Respiroception} - Resp;
\emph{Signalling} - Sign; \emph{Gastroception} - Gast; \emph{Dermal
Hypersensitivity} - Derm; \emph{Sexual Arousal Changes} - SexC).

To further reduce and balance the remaining items, we collectively
decided on removing the lower-level clusters \emph{Sexual Arousal
Awareness} (too general and overlapping with the other more specific
sex-related items), \emph{Signalling} (which items started with ``when
something important is happening in my life'', which meaning we deemed
too much open to interpretation), and \emph{Sexual Arousal Changes} (low
fit with the other modality-focused clusters of its group). The final
set included 45 items.

@@

Possible (although not at all significant) bias consistent across
indices in favour of a greater similarity with the modality-grouping
condition.

\section{Study 2: Validation}\label{study-2-validation}

TODO: write intro. Goal of study 2: to validate the Mint scale against
other interoception scales.

\subsection{Methods}\label{methods-1}

\subsubsection{Participants}\label{participants-1}

We recruited 921 English-speaking participants via
Prolific\textcopyright and SONA, from which 118 were excluded for
failing at least one attention check and 6 based on multivariate
distance (using the same procedure as for study 1). 60 participants were
further excluded due to missing data following a technical error. The
final sample includes 737 participants (age = 36.8 \(\pm\) 14.7 {[}18,
87{]}; 57.3\% women; Country of residence: 75.17\% United Kingdom,
24.83\% other). This study was approved by the University of Sussex'
Ethics Committee (\textbf{NUMBER}).

\subsubsection{Procedure}\label{procedure-1}

The experiment included the following questionnaires.

\paragraph{Interoception
Questionnaires.}\label{interoception-questionnaires}

\subparagraph{The Multimodal Interoception Questionnaire
(Mint).}\label{the-multimodal-interoception-questionnaire-mint}

The 45 items of the Mint scale were presented in a random order, with
the same 7-point Likert scale as in study 1 (0 = Disagree, 6 = Agree).

\subparagraph{Multidimensional Assessment of Interoceptive Awareness
(MAIA).}\label{multidimensional-assessment-of-interoceptive-awareness-maia}

The X items of the MAIA\ldots{}

\subparagraph{The Body Perception Questionnaire
(BPQ).}\label{the-body-perception-questionnaire-bpq}

\textbf{TODO}

\subparagraph{The Interoceptive Awareness Scale
(IAS).}\label{the-interoceptive-awareness-scale-ias}

\textbf{TODO}

\paragraph{Emotions and Cognition.}\label{emotions-and-cognition}

\subparagraph{Toronto Alexithymia Scale
(TAS-20).}\label{toronto-alexithymia-scale-tas-20}

\textbf{TODO}

\subparagraph{Emotion Reactivity Scale
(ERS).}\label{emotion-reactivity-scale-ers}

\textbf{TODO}

\subparagraph{Cognitive Emotion Regulation Questionnaire
(CERQ).}\label{cognitive-emotion-regulation-questionnaire-cerq}

\textbf{TODO}

\subparagraph{TODO (CEFSA).}\label{todo-cefsa}

\textbf{TODO}

\subparagraph{Primal World Beliefs
(PI-18).}\label{primal-world-beliefs-pi-18}

\textbf{TODO}

\paragraph{Health and Wellbeing.}\label{health-and-wellbeing}

\subparagraph{Life Satisfaction, Depression and Anxiety
(PHQ-4).}\label{life-satisfaction-depression-and-anxiety-phq-4}

\textbf{TODO}

\subparagraph{Mental Health.}\label{mental-health}

Participants were asked to self-report any current, medically diagnosed
psychiatric disorders using a checklist based on DSM-5 categories. If
one or more conditions were endorsed, participants were asked to
indicate any current treatments, including pharmacological (e.g.,
antidepressants, anxiolytics, antipsychotics, mood stabilizers),
psychological (e.g., psychotherapy, mindfulness), or lifestyle
interventions. Binary variables (0 = absent, 1 = present) were created
to identify participants reporting mood disorders (MDD, GAD, Bipolar
Disorder; with a stricter subgroup of participants undergoing a pharma-
or psychological treatment), anxiety-centred disorders (GAD, Panic
Disorder, Social Anxiety Disorder, Specific Phobias), eating disorders,
addiction-related disorders, borderline personality disorder, autism
spectrum disorder (ASD), and ADHD.

\subparagraph{Somatic Health.}\label{somatic-health}

Participants were asked to select somatic symptoms or conditions they
experienced from a list of 36 options. To facilitate mechanistic
interpretation and reduce redundancy, answers were grouped into four
non-overlapping clusters based on shared physiological pathways and
known etiological mechanisms. The \emph{Afferent Sensitivity} cluster
included conditions associated with heightened interoceptive awareness
and neurogenic excitability, such as migraine, neuropathy, dizziness,
nausea, muscle tension, epilepsy, and frequent urination. The
\emph{Central Sensitization} cluster comprised syndromes characterized
by chronic pain and fatigue, likely reflecting central amplification of
sensory signals and HPA-axis dysregulation, such as fibromyalgia,
chronic fatigue syndrome, chronic pain, back pain, pelvic pain,
irritable bowel syndrome (IBS). The \emph{Autonomic Dysfunction} cluster
captured disorders linked to dysregulation of the autonomic and
cardiopulmonary systems, including joint hypermobility, cardiac
arrhythmia, chest pain, shortness of breath, hypo-/hypertension, sleep
apnea, chronic obstructive pulmonary disease (COPD), and chronic
bronchitis. Finally, the \emph{Immune-Inflammatory} cluster encompassed
conditions associated with immune dysregulation, barrier dysfunction,
and gut-brain axis disturbance, such as eczema, psoriasis, skin rashes,
asthma, celiac disease, gluten and lactose sensitivity, inflammatory
bowel diseases (Crohn's disease and ulcerative colitis),
gastroesophageal reflux disease (GERD), multiple sclerosis, and
Sjögren's syndrome. We scored each cluster as a binary variable based on
whether the participant selected at least one symptom from that cluster.

\paragraph{Lifestyle.}\label{lifestyle}

\textbf{TODO}

Physical activity.

Wearables.

\paragraph{Randomization.}\label{randomization}

In order to avoid the repetition of similar types of questions and and
balance longer and shorter questionnaires, we partitioned them into
three groups (and randomized their order within them): (1) interoception
questionnaires (MAIA, IAS, BPQ), (2) emotions (TAS, CERQ, ERS, PI-18),
and (3) pathology (somatic health, mental health, LS + PHQ-4, CEFSA).
After completing demographic questions, participants always started with
the Mint scale, and each following interoception questionnaire was
interspersed with two questionnaires from the emotions and pathology
groups. In order to make the experiment more enjoyable, the experiment
ended with a radar chart summarizing the participants' responses to the
Mint scale\footnote{The experiment can be tested by following the link
  on https://github.com/RealityBending/InteroceptionScale}.

\subsubsection{Data Analysis}\label{data-analysis-1}

We will start by confirming and further refining the structure of the
Mint scale using the same EGA model as in Study 1. The convergent
validity of the final set of items will be assessed by computing the
correlations between the Mint scale and the other interoception
questionnaires (MAIA, BPQ, IAS). Then, we will test the predictive power
of the Mint scale (relative to the other interoception questionnaires)
on various measures. We will start by fitting regression (linear for
continuous measures - e.g., depression score - and logistic for binary

{\caption{{TODO.}{\label{fig-two}}}}

\begin{center}
\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{../study2/analysis/figures/fig1.png}
\end{center}

\subsection{Results}\label{results-1}

{\caption{{TODO.}{\label{fig-three}}}}

\begin{center}
\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{../study2/analysis/figures/table1.png}
\end{center}

{\caption{{TODO.}{\label{fig-four}}}}

\begin{center}
\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{../study2/analysis/figures/fig2.png}
\end{center}

{\caption{{TODO.}{\label{fig-five}}}}

\begin{center}
\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{../study2/analysis/figures/fig3.png}
\end{center}

{\caption{{TODO.}{\label{fig-six}}}}

\begin{center}
\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{../study2/analysis/figures/table2.png}
\end{center}

\subsection{Discussion}\label{discussion-1}

\section{General Discussion}\label{general-discussion}

@@

\phantomsection\label{refs}
\begin{CSLReferences}{1}{0}
\bibitem[\citeproctext]{ref-christensen2023unique}
Christensen, A. P., Garrido, L. E., \& Golino, H. (2023). Unique
variable analysis: A network psychometrics method to detect local
dependence. \emph{Multivariate Behavioral Research}, \emph{58}(6),
1165--1182.

\bibitem[\citeproctext]{ref-christensen2021equivalency}
Christensen, A. P., \& Golino, H. (2021). On the equivalency of factor
and network loadings. \emph{Behavior Research Methods}, \emph{53}(4),
1563--1580.

\bibitem[\citeproctext]{ref-de2015jspsych}
De Leeuw, J. R. (2015). jsPsych: A JavaScript library for creating
behavioral experiments in a web browser. \emph{Behavior Research
Methods}, \emph{47}, 1--12.

\bibitem[\citeproctext]{ref-golino2017exploratory}
Golino, H. F., \& Epskamp, S. (2017). Exploratory graph analysis: A new
approach for estimating the number of dimensions in psychological
research. \emph{PloS One}, \emph{12}(6), e0174035.

\bibitem[\citeproctext]{ref-golino2020investigating}
Golino, H., Shi, D., Christensen, A. P., Garrido, L. E., Nieto, M. D.,
Sadana, R., Thiyagarajan, J. A., \& Martinez-Molina, A. (2020).
Investigating the performance of exploratory graph analysis and
traditional techniques to identify the number of latent factors: A
simulation and tutorial. \emph{Psychological Methods}, \emph{25}(3),
292.

@@

\bibitem[\citeproctext]{ref-jimenez2023dimensionality}
Jiménez, M., Abad, F. J., Garcia-Garzon, E., Golino, H., Christensen, A.
P., \& Garrido, L. E. (2023). Dimensionality assessment in bifactor
structures with multiple general factors: A network psychometrics
approach. \emph{Psychological Methods}.

### 2025-07-01 study1/analysis/1_cleaning.qmd
lesgoo

```{r}
df |> 
  summarise(n = n(), .by=c("Condition", "Experiment_Enjoyment")) |>
  filter(!is.na(Experiment_Enjoyment)) |> 
  mutate(n = n / sum(n),
         Experiment_Enjoyment = fct_rev(as.factor(Experiment_Enjoyment)),
         .by="Condition") |>
  ggplot(aes(y = Condition, x = n, fill = Experiment_Enjoyment)) +
  geom_bar(stat="identity", position="stack") +
  scale_fill_manual(values=c("green", "yellowgreen",  "yellow", "orange", "red")) +
  scale_x_continuous(expand=c(0, 0))  +
  labs(title="Experiment Enjoyment",
       subtitle="Proportion of participants by condition") + 
  guides(fill = guide_legend(reverse=TRUE)) +
  theme_minimal() +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        legend.position = "top",
        legend.title = element_blank())

>>>>

```{r}
df |> 
  summarise(n = n(), .by=c("Condition", "Experiment_Enjoyment")) |>
  filter(!is.na(Experiment_Enjoyment)) |> 
  mutate(n = n / sum(n),
         Experiment_Enjoyment = fct_rev(as.factor(Experiment_Enjoyment)),
         .by="Condition") |>
  mutate(Condition = str_replace(Condition, "Domains", "By Modality"),
         Condition = str_replace(Condition, "Dimensions", "By Facet"),
         Condition = str_replace(Condition, "Random", "Randomly")) |>
  ggplot(aes(y = Condition, x = n, fill = Experiment_Enjoyment)) +
  geom_bar(stat="identity", position="stack") +
  scale_fill_manual(values=c("green", "yellowgreen",  "yellow", "orange", "red")) +
  scale_x_continuous(expand=c(0, 0))  +
  labs(title="Experiment Enjoyment",
       subtitle="Proportion of participants by condition", 
       y = "Items presented grouped...") + 
  guides(fill = guide_legend(reverse=TRUE)) +
  theme_minimal() +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        legend.position = "top",
        legend.title = element_blank())

### 2025-07-01 study1/analysis/2_analysis.qmd
lesgoo

set.seed(42)
```

@@

bootstrap_similarity <- function(df) {
  rez <- data.frame()
  for(i in 1:200) {
    idx <- sample(1:nrow(df), nrow(df), replace=TRUE)
    newdata <- df[idx,]
    items <- select(df, contains("_Q"))
    byfacet <- items[newdata$Condition=="Dimensions",]
    bymodality <- items[newdata$Condition=="Domains",]
    byrandom <- items[newdata$Condition=="Random",]

@@

rez[rez$Comparison ==  "Random vs. Facet",  "d_PSI"] |> 
  pd()
rez[rez$Comparison ==  "Random vs. Facet" & rez$Sample == "Random",  "d_PSI"] |> 
  pd()

rez |> 
  summarize(PSI = mean(PSI),
            p_PSI = as.numeric(bayestestR::pd(d_PSI, as_p=TRUE)),
            RVadj = mean(RVadj),
            p_RVadj = as.numeric(bayestestR::pd(d_RVadj, as_p=TRUE)),
            SMI = mean(SMI),
            p_SMI = as.numeric(bayestestR::pd(d_SMI, as_p=TRUE)),
            .by = "Comparison")
```

@@

fig1 <- p1 / (p3 | p_sim | p2) +
  patchwork::plot_layout(heights=c(3, 1)) +
  patchwork::plot_annotation(
    title="Effect of Item Grouping",
    theme = theme(plot.title = element_text(hjust = 0.5, face="bold")))
fig1

@@

@@

# Remove items
toremove2 <- filter(itemstability_table, Max < 0.8)$Item
toremove2 <- itemstability_table |> 
  filter(!Item %in% toremove2) |>
  mutate(Item, n=n(), .by="Cluster", .keep="used") |> 
  filter(n < 3) |>  # Remove small clusters
  pull(Item) |> 
  c(toremove2)
```

@@

## Structure Analysis

@@

@@

@@

gt::gtsave(gt::cols_hide(tab1, `|`), "table1.html", inline_css = TRUE) # Save it and reload it otherwise formatting not ideal

Sys.setenv(CHROMOTE_CHROME = "C:\\Program Files (x86)\\Microsoft\\Edge\\Application\\msedge.exe")

gt::gtsave(tab1, "table1.png", vwidth=1660, expand=0, quiet=TRUE)
```

@@

# EGAnet::EGM(items[, 1:60])
EGAnet::EGM.compare(items, model = "glasso", algorithm = "leiden")
rez <- EGAnet::network.compare(byfacet, bymodality, model = "glasso", seed=3)

>>>>

set.seed(42)

Sys.setenv(CHROMOTE_CHROME = "C:\\Program Files (x86)\\Microsoft\\Edge\\Application\\msedge.exe")
```

@@

bootstrap_similarity <- function(df) {
  rez <- data.frame()
  for(i in 1:500) {
    idx <- sample(1:nrow(df), nrow(df), replace=TRUE)
    newdata <- df[idx,]
    items <- select(df, contains("_Q"))
    byfacet <- items[newdata$Condition=="Dimensions",]
    bymodality <- items[newdata$Condition=="Domains",]
    byrandom <- items[newdata$Condition=="Random",]

@@

```{r}
rez |> 
  summarize(PSI = mean(PSI),
            p_PSI = as.numeric(bayestestR::pd(d_PSI, as_p=TRUE)),
            RVadj = mean(RVadj),
            p_RVadj = as.numeric(bayestestR::pd(d_RVadj, as_p=TRUE)),
            SMI = mean(SMI),
            p_SMI = as.numeric(bayestestR::pd(d_SMI, as_p=TRUE)),
            .by = "Comparison")
```

@@

fig1 <- p1 / (p3 | p_sim | p2) +
  patchwork::plot_layout(heights=c(3, 1)) +
  patchwork::plot_annotation(
    title="Item Correlation Matrix Similarity",
    theme = theme(plot.title = element_text(hjust = 0.5, face="bold")))
fig1

@@

We removed `r length(toremove1)` items (`r paste(toremove1, collapse=", ")`) based on Unique Variable Analysis (UVA).

@@

# Remove items
toremove2 <- filter(itemstability_table, Max < 0.8)$Item
```

We removed `r length(toremove2)` items (`r paste(toremove2, collapse=", ")`) that had a low stability (< 0.8).

```{r}
toremove2b <- itemstability_table |> 
  filter(!Item %in% toremove2) |>
  mutate(Item, n=n(), .by="Cluster", .keep="used") |> 
  filter(n < 3) |>  # Remove small clusters
  pull(Item)

toremove2 <- c(toremove2, toremove2b)
```

We removed `r length(toremove2b)` items (`r paste(toremove2b, collapse=", ")`) that were in clusters with less than 3 items after the first removal.

@@

We kept the 3 items with the highest loading in their lower-level structure, removing `r length(toremove3)` items (`r paste(toremove3, collapse=", ")`).

## Structure Analysis (Final Selection)

### EGA

@@

```{r}
EGAnet::genTEFI(ega3$EGA)
# cfa <- EGAnet::CFA(ega3$EGA, 
#             items[colnames(ega3$lower_order$boot.wc)],
#             estimator = "WLSMV")
```

@@

``` 
```{r}
#| message: false

@@

gt::gtsave(gt::cols_hide(tab1, `|`), "figures/table1.html", inline_css = TRUE) # Save it and reload it otherwise formatting not ideal

gt::gtsave(tab1, "figures/table1.png", vwidth=1660, expand=0, quiet=TRUE)
```

@@

# EGAnet::EGM(items[, 1:60])
# EGAnet::EGM.compare(items, model = "glasso", algorithm = "leiden")
rez <- EGAnet::network.compare(byfacet[colnames(ega3$lower_order$boot.wc)], 
                               bymodality[colnames(ega3$lower_order$boot.wc)], 
                               model = "glasso", seed=3)
